### 2015-12-30 Projects/DelCo_2012/Report/DelCo_2012.tex
update cafs report

To compare the effectiveness of the suppression agents (CAFS, water), the temperatures from the thermocouple tree which was not directly impacted by the streams was analyzed. Thermocouples that were greater than 2.13~m (7~ft) below the ceiling (the bottom 3 thermocouples) were not included because of the minimal temperature readings throughout the tests. Gas cooling was determined by taking the normalized maximum change in temperature ($\hat{T}$) over the test interval ($T_{max}$ is peak temperature before suppression and $T_{min}$ is minimum temperature after suppression):
\begin{equation}
\label{eq:norm_temp}
\hat{T} = \frac{T_{max}-T_{min}}{T_{max}}
\end{equation}
The normalized temperature difference is taken because of the large variation in pre-suppression temperature within replicates of a particular suppression agent and between suppression agents.

@@

>>>>

To compare the effectiveness of the suppression agents (CAFS, water), the temperatures from the thermocouple tree which was not directly impacted by the streams was analyzed. Thermocouples that were greater than 2.13~m (7~ft) below the ceiling (the bottom 3 thermocouples) were not included because of the minimal temperature readings throughout the tests. Gas cooling was determined by taking the normalized maximum change in temperature ($\hat{T}$) over the test interval ($T_{max}$ is peak temperature before suppression and $T_{min}$ is minimum temperature after suppression):
\begin{equation}
\label{eq:norm_temp}
\hat{T} = \frac{T_{max}-T_{min}}{T_{max}}
\end{equation}
The normalized temperature difference is taken because of the variation in pre-suppression temperature within replicates of a particular suppression agent and between suppression agents.

For the 7/8~in solid stream tests there were 7 replicate conducted for both water and CAFs suppression. The normalized temperature differences for the 8 thermocouples analyzed from the water experiments were compared against the same normalized temperature differences from the CAFs tests. These data points are visualized through a scatterplot, Fig.~\ref{fig:CAFS_Water_Comp_7_8}.

@@

The circles in Fig.~\ref{fig:CAFS_Water_Comp_7_8} are the normalized temperature measure points. If water and CAFs had the exact same normalized temperature differences, all of the points would fall along solid black line in the figure. Circles that vary from that line represent measurements where either water or CAFS cooled more signifcantly than the other agent. The gray area surrounding the solid black line, represents measurment uncertainty (\ref{subsec:Uncertainty}). For data that fall within this area, there is an inability to determine which agent was more or less effective than the other. The red dashed line is the line the fits the data representing the minimal difference between the two suppression agents by a linear approximation of the data. Since this line falls within the gray area there is an inability to distinguish, with statistical confidence, a difference between water or CAFs to cool gases from a 7/8~in solid stream.

The second water and CAFs comparison was to examine 5 replicate tests for a straight stream in the mid-position, Fig.~\ref{fig:CAFS_Water_Comp_SS_mid}. The same analysis was performed for this configuration. These results also indicate that there is
